Overconfidence and settlement: evidence from Mexican labor courts\thanks{We would like to thank Sebastian Garcia, Isaac Meza, Diana Roman, and Monica Zamudio (``la banda pesada'' and ``los mas aca'') for superhuman research assistance. All errors are ours.}

### 2017-08-01 Paper/main.tex
Todos los pendientes del mail del 26 julio 2017

@@

\begin{figure}[H]
    \caption{Belief updating after treatment}
    \label{Figure_updating}
    \begin{center}
%    \begin{subfigure}{\textwidth}
%        \caption{update in beliefs in duration}
%        \centering
%        \includegraphics[width=\textwidth]{updatebeleif_duration.pdf}
%    \end{subfigure}
    \begin{subfigure}{\textwidth}
        \caption{Update in beliefs in amount}
        \centering
        \includegraphics[width=\textwidth]{updatebeleif_amount.pdf}
    \end{subfigure}
    \end{center}
     \footnotesize \textit{Notes: Graphs on belief updating. They show the following statistic: $\theta=\left|\frac{P-exitsurvey}{P-initialsurvey}\right|$. Where $P$ is the prediction made by the calculator and $exit$ and $initial$ survey variables denote what each part answered on the survey for amount won. Note that when $\theta=1$ we have no update with respect to the prediction. And when $\theta<1$ they update in the direction of what calculator says. The extreme case $\theta=0$ implies perfect updating with respect to what the calculator says.} 
      \footnotesize{ \textit{Do file: }  \texttt{Update\_beleifs.do}}
\end{figure}

@@

@@

@@

@@

>>>>

\begin{table}[H]
\caption{Determinants of overconfidence}
\label{Table_determinantsOC}
\begin{center}
\scriptsize{\input{./Tables/oc_reg_theta.tex}}
\end{center}
 \footnotesize
\textit{Notes:} 
\emph{Mistreated} variable refers to the survey question: "How well do you think you were treated by the firm?". The omitted category is "Very Good", while 1, 2 and 3 refer to "Fairly Well", "Not so well" and "Not well at all".
Omited variable for \emph{education} is elementary education, while for \emph{Mistreated} is very good, and the scale is increasing, i.e. the worker feels more mistreated . We use the following statistic to measure overconfidence: $\theta=\left|\frac{P-exitsurvey}{P-initialsurvey}\right|$. Where $P$ is the prediction made by the calculator and $exit$ and $initial$ survey variables denote what each part answered on the survey for amount won. Note that when $\theta=1$ we have no update with respect to the prediction. And when $\theta<1$ they update in the direction of what calculator says. The extreme case $\theta=0$ implies perfect updating with respect to what the calculator says.
\textit{Do file: } \texttt{oc\_reg\_theta.do}
\end{table}

@@

\begin{figure}[H]
    \caption{Belief updating after treatment}
    \label{Figure_updating}
    \begin{center}
%    \begin{subfigure}{\textwidth}
%        \caption{update in beliefs in duration}
%        \centering
%        \includegraphics[width=\textwidth]{updatebeleif_duration.pdf}
%    \end{subfigure}
    \begin{subfigure}{\textwidth}
        \caption{Update in beliefs in amount}
        \centering
        \includegraphics[width=\textwidth]{updatebeleif_amount_1.pdf}
    \end{subfigure}

        \begin{subfigure}{\textwidth}
        \caption{Update in beliefs in amount (Scale Up)}
        \centering
        \includegraphics[width=\textwidth, height=0.25\textheight]{updatebeleif_amount_2.pdf}
    \end{subfigure}

    \end{center}
     \footnotesize \textit{Notes: Graphs on belief updating. They show the following statistic: $\theta=\left|\frac{P-exitsurvey}{P-initialsurvey}\right|$. Where $P$ is the prediction made by the calculator and $exit$ and $initial$ survey variables denote what each part answered on the survey for amount won. Note that when $\theta=1$ we have no update with respect to the prediction. And when $\theta<1$ they update in the direction of what calculator says. The extreme case $\theta=0$ implies perfect updating with respect to what the calculator says. This graph only considers observations that falls between 0 and 1; and the \% of the observations that fall in that range are indicated below. The stars above the mean indicates the p-value, testing the mean equal 1.} 
      \footnotesize{ \textit{Do file: }  \texttt{Update\_beleifs.do}}
\end{figure}

@@

\begin{table}[H]
    \caption{Direct Updating}
    \begin{subtable}{.5\linewidth}
      \centering
        \caption{Pilot}
        \scriptsize{\input{./Tables/update_beleif_1.tex}}
    \end{subtable}%
    \begin{subtable}{.5\linewidth}
      \centering
        \caption{Scale Up}
        \scriptsize{\input{./Tables/update_beleif_2.tex}}
    \end{subtable} 
           \footnotesize    
  \textit{Notes:} 
    Summary statistics of parties' update in beliefs; measured as $\frac{exit-initial}{initial}$, for both \emph{Pilot} and \emph{Scale Up}.
    \textit{Do file: } \texttt{update\_beleif\_ss.do}
\end{table}

@@

\begin{table}[H]
    \caption{Correlation conciliation vs overconfidence}
    \label{Table_concvsoc_theta}
    \begin{center}
        \scriptsize{\input{./Tables/Reg_con_oc_theta.tex}}
    \end{center}
    \footnotesize
    \textit{Notes:} 
   We use the following statistic to measure overconfidence: $\theta=\left|\frac{P-exitsurvey}{P-initialsurvey}\right|$. Where $P$ is the prediction made by the calculator and $exit$ and $initial$ survey variables denote what each part answered on the survey for amount won.. Elastictity : Con-OC measures how much does conciliation change when overconfidence changes in 1 standard deviation. Elasticity SD:Con-OC measures how many standard deviations conciliation changes when  overconfidence changes in 1 standard deviation.
    \textit{Do file: } \texttt{con\_vs\_oc\_theta.do}
\end{table}

\begin{landscape}
\begin{table}[H]
    \caption{Conciliation and updating}
    \label{Con_update}
    \begin{center}
        \scriptsize{\input{./Tables/con_vs_update.tex}}
    \end{center}
    \footnotesize
    \textit{Notes:} 
   The following table displays a regression of conciliation against the statistics of updating $\theta=\left|\frac{P-exitsurvey}{P-initialsurvey}\right|$
    \textit{Do file: } \texttt{con\_vs\_update.do}
\end{table}
\end{landscape}

@@

\begin{landscape}
\begin{table}[H]
    \caption{ITT and ATT}
    \label{ITT_ATT}
    \begin{center}
    \scriptsize{\input{./Tables/ITT_ATT.tex}}
    \end{center}
    \footnotesize
    \textit{Notes:}

    \textit{Do file: } \texttt{ITT\_ATT.do}
\end{table}
\end{landscape}

@@

\begin{figure}[H]
    \caption{Belief updating after treatment}
    \label{Figure_updating}
    \begin{center}
    \begin{subfigure}{\textwidth}
        \caption{Update in beliefs in amount (Pilot) }
        \centering
        \includegraphics[width=\textwidth]{updatebeleif_amount_total_1.pdf}
    \end{subfigure}

        \begin{subfigure}{\textwidth}
        \caption{Update in beliefs in amount (Scale Up) }
        \centering
        \includegraphics[width=\textwidth, height=0.25\textheight]{updatebeleif_amount_total_2.pdf}
    \end{subfigure}
    \end{center}
     \footnotesize \textit{Notes: Graphs on belief updating. They show the following statistic: $\theta=\left|\frac{P-exitsurvey}{P-initialsurvey}\right|$. Where $P$ is the prediction made by the calculator and $exit$ and $initial$ survey variables denote what each part answered on the survey for amount won. Note that when $\theta=1$ we have no update with respect to the prediction. And when $\theta<1$ they update in the direction of what calculator says. The extreme case $\theta=0$ implies perfect updating with respect to what the calculator says. This graph considers all observations but some outliers; the \% of the observations considered are indicated below. The stars above the mean indicates the p-value, testing the mean equal 1.} 
      \footnotesize{ \textit{Do file: }  \texttt{Update\_beleifs\_total.do}}
\end{figure}
